---
Samuel Gitau
Week 13 IP
---
## Overview
In this project, we will be working with Kira Plastinina- a Russian brand that is sold through a defunct chain of retail stores in Russia, Ukraine, Kazakhstan, Belarus, China, Philippines, and Armenia. The brand’s Sales and Marketing team would like to understand their customer’s behavior from data that they have collected over the past year. More specifically, they would like to learn the characteristics of customer groups.

## Installing important packages----
```{r}
install.packages("dplyr")
library(dplyr)
install.packages("tidyr")
library(tidyr)
install.packages("ggplot2")
library(ggplot2)
install.packages("tibble")
library(tibble)
install.packages("Hmisc")
library('Hmisc')
install.packages("pander")
library(pander)
install.packages("corrplot")
library(corrplot)
install.packages("magrittr")
library(magrittr)
install.packages("sos")
library(sos)
findFn("select")
install.packages("data.table")
library(data.table)
install.packages("knitr")
library(knitr)
```
## Loading the dataset ----
```{r}
df <- read.csv("shoppers.csv")
```
###Previewing the first 6 rows 
```{r}
head(df)
```
###Previewing the last 6 rows
```{r}
tail(df)
```
#checking shape of the dataset
```{r}
dim(df)
```
## Checking Information  our dataset----
###Checking number of columns 
```{r}
colnames(df)
```
```{r}
install.packages("tibble")
library(tibble)
df <- as.tibble(df)
df
```
###Checking summary statistics of our dataset
```{r}
summary(df)
```
## Cleaning the Dataset----
###Check for missing values
```{r}
colSums(is.na(df))
```
 ###dropping null values
```{r}
df_new<-na.omit(df)
colSums(is.na(df_new))
dim(df_new)
```
Converting boolean  to numerical 
```{r}
num <- c("Revenue", "Weekend" )
df_new[num] <- sapply(df_new[num],as.numeric)
sapply(df_new, class)
```
###checking for duplicated values and removing them
```{r}
duplicated_rows <- df_new[duplicated(df_new),]
df_new <- unique(df_new)
dim(df_new)

```
selecting numerical 
```{r}
num <- dplyr::select_if(df_new, is.numeric)
head(num)
```
```{r}
colnames(num)
```
##EDA----
Univariate Analysis
```{r}
install.packages("ggplot2")
library(ggplot2)
ggplot(num) + geom_bar(aes(x = Revenue),fill = 'blue')
```
There were more false values compared to true
###Bivariate analysis
we will compare the other factors to revenue
```{r Fig2}
A <- ggplot(num , mapping = aes(x = Administrative_Duration,fill = Revenue , color = Revenue )) +
         geom_histogram() + labs(title = "Administrative_Duration Distribution by  Revenue")
A 
B <- ggplot(num , mapping = aes(x = Informational_Duration,fill = Revenue , color = Revenue )) +
         geom_histogram() + labs(title = "Informational_Duration Distribution by  Revenue")
B 
C <- ggplot(num , mapping = aes(x = ProductRelated ,fill = Revenue , color = Revenue )) +
         geom_histogram() + labs(title = "ProductRelated Distribution by  Revenue")
C + theme_bw()
D <- ggplot(num , mapping = aes(x = ProductRelated_Duration,fill = Revenue , color = Revenue )) +
         geom_histogram() + labs(title = "ProductRelated_Duration Distribution by  Revenue")
D 
E <- ggplot(num , mapping = aes(x = BounceRates,fill = Revenue , color = Revenue )) +
         geom_histogram() + labs(title = "Bounce Rates Distribution by  Revenue")
E 
G <- ggplot(num , mapping = aes(x = ExitRates ,fill = Revenue , color = Revenue )) +
         geom_histogram() + labs(title = "ExitRates Distribution by  Revenue")
G 
H <- ggplot(num , mapping = aes(x = PageValues ,fill = Revenue , color = Revenue )) +
         geom_histogram() + labs(title = "PageValues Distribution by  Revenue")
H 
```
```{r Fig1, fig.height=5, fig.width= 10}
par(mfrow=c(8,1))
ggplot(num , mapping = aes(x = Administrative, color = Revenue )) +
         geom_freqpoly() + labs(title = "Administrative Distribution by Revenue")
ggplot(num , mapping = aes(x = Informational, color = Revenue )) +
         geom_freqpoly() + labs(title = "Informational Distribution by Revenue")
ggplot(num , mapping = aes(x = SpecialDay, color = Revenue )) +
         geom_freqpoly() + labs(title = "SpecialDay Distribution by Revenue")
ggplot(num , mapping = aes(x = OperatingSystems, color = Revenue )) +
         geom_freqpoly() + labs(title = "OperatingSystems Distribution by Revenue")
ggplot(num , mapping = aes(x = Browser, color = Revenue )) +
         geom_freqpoly() + labs(title = "Browser Distribution by Revenue")
ggplot(num , mapping = aes(x = Region, color = Revenue )) +
         geom_freqpoly() + labs(title = "Region Distribution by Revenue")
ggplot(num , mapping = aes(x = TrafficType, color = Revenue )) +
         geom_freqpoly() + labs(title = "TrafficType Distribution by Revenue")
ggplot(num , mapping = aes(x = Weekend, color = Revenue )) +
         geom_freqpoly() + labs(title = "Weekend Distribution by Revenue")
```
finding correlation 
```{r}
install.packages("Hmisc")
library('Hmisc')
res <- rcorr(as.matrix(num))
corr <- data.frame(res$r)
corr
```
```{r, fig.height=10, fig.width= 10}
corrplot(res$r,  order = "hclust", 
         tl.col = "black", tl.srt = 45)
```
```{r}
plot <- data.frame(corr$Revenue)
rownames(plot) <- colnames(corr)
plot
```
##Building models----
###Feature selection
We will only select features with positive correlation
```{r}
column <- c('Administrative', 'Administrative_Duration',"Informational", "Informational_Duration",
            "ProductRelated", "ProductRelated_Duration", "PageValues", "Browser", "Weekend")
df <- num[column]
head(df)
```
###K-Means Clustering---
```{r}
target <- num$Revenue
```
scale our Features dataframe
```{r}
# We define a normal function which will normalize the set of values according to its minimum value and maximum value.
normal <- function(x) (
  return( ((x - min(x)) /(max(x)-min(x))) )
)
normal(1:9)
df_model1 <- as.data.frame(lapply(df, normal))
summary(df_model1)
```
Applying the K-means clustering (k)=3
```{r}
result<- kmeans(df_model1,3) 
```
Checking the records in each cluster
```{r}
result$size
```
Getting the value of cluster center datapoint value
```{r}
result$centers 
```
Getting the cluster vector 
```{r}
head(result$cluster)
tail(result$cluster)
```
clustering results
```{r}
par(mfrow = c(1,2), mar = c(5,4,2,2))
plot(df_model1[,1:2], col = result$cluster) 
plot(df_model1[,3:4], col = result$cluster) 
```
Verifying the results of clustering
```{r}
table(result$cluster, target)
```

