---
Samuel Gitau
Week 13 IP
---

## Installing important packages----
```{r}
install.packages("dplyr")
library(dplyr)
install.packages("tidyr")
library(tidyr)
install.packages("ggplot2")
library(ggplot2)
install.packages("tibble")
library(tibble)
install.packages("Hmisc")
library('Hmisc')
install.packages("pander")
library(pander)
install.packages("corrplot")
library(corrplot)
install.packages("magrittr")
library(magrittr)
install.packages("sos")
library(sos)
findFn("select")
install.packages("data.table")
library(data.table)
install.packages("knitr")
library(knitr)
```
## Loading the dataset ----
```{r}
df <- read.csv("shoppers.csv")
```
###Previewing the first 6 rows 
```{r}
head(df)
```
###Previewing the last 6 rows
```{r}
tail(df)
```
#checking shape of the dataset
```{r}
dim(df)
```
## Checking Information  our dataset----
###Checking number of columns 
```{r}
colnames(df)
```
```{r}
df <- as.tibble(df)
df
```
###Checking summary statistics of our dataset
```{r}
summary(df)
```
## Cleaning the Dataset----
###Check for missing values
```{r}
colSums(is.na(df))
```
###checking for duplicated values
```{r}
duplicated_rows <- df[duplicated(df),]
duplicated_rows
```
###Checking for outliers
####Getting the numerical columns
```{r}
install.packages("MASS")
library(MASS)
install.packages("dplyr")
library(dplyr)
df_num <- (df %>% select(c("Daily.Time.Spent.on.Site", "Area.Income", "Age", "Daily.Internet.Usage")))
```